Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-22 analysis/paper/paper.Rmd
Fixes figure order, closes #54
Closes #54, corrects figure order, filenames and subfigure designations

Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)i).
Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.

More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure  \@ref(fig:articleScores)ii).

Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)iii).

However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)iv).

@@

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

rrpp <- import_notes()
theme_set(theme_classic())
i <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar() +
  ylab("Score") +
  xlab(NULL)

ii <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar() +
  xlab(NULL) +
  ylab(NULL)

iii <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar() +
  ylab("Score")

iv <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar() +
  ylab(NULL)

# put them all together
p <- (i | ii) / (iii | iv)
p <- p + plot_annotation(tag_levels = "i")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       device = "eps",
       width = 6,
       height = 6,
       units = "in")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

>>>>

Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.

More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure  \@ref(fig:articleScores)B).

Software citations were also reasonably well reported in the literature with 120 scoring '2' where the main software was cited with version numbers and 57 scoring '3' where full citations including R packages or the SAS PROC used were cited where appropriate (Figure \@ref(fig:articleScores)C).

However, data availability was mostly not available with 243 or 81.5% scoring 0' where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored '3' than '1' or '2' combined, with two articles not producing shareable data (Figure \@ref(fig:articleScores)D).

@@

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar() +
  ylab("Score") +
  xlab(NULL)

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar() +
  xlab(NULL) +
  ylab(NULL)

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar() +
  ylab("Score")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar() +
  ylab(NULL)

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A")
ggsave(filename = "../figures/Sparks et al Figure 1.eps",
       plot = p,
       device = "eps",
       width = 6,
       height = 6,
       units = "in")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 2.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("figures/Sparks et al Figure 2eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```
